\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-06-12 doc/src/CSRs.tex
Fix stupid typo
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

If extension Smcsrind if also implemented, then when \z{miselect}
has a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts to access alias CSRs \z{mireg2} through \z{mireg6}
raise an illegal instruction exception.

@@

If extension Sscsrind if also implemented, then when \z{siselect}
has a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts to access alias CSRs \z{sireg2} through \z{sireg6}
raise an illegal instruction exception (unless executing
in a virtual machine, covered in the next section).

@@

If extension Sscsrind if also implemented, then when \z{vsiselect} has
a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts from privilege modes other than VS or VU to access alias CSRs
\z{vsireg2} through \z{vsireg6} raise an illegal instruction exception,
and attempts from VS or \mbox{VU-mode} to access \z{sireg2}
through \z{sireg6} or \z{vsireg2} through \z{vsireg6}
raise a virtual instruction exception.

>>>>

If extension Smcsrind is also implemented, then when \z{miselect}
has a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts to access alias CSRs \z{mireg2} through \z{mireg6}
raise an illegal instruction exception.

@@

If extension Sscsrind is also implemented, then when \z{siselect}
has a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts to access alias CSRs \z{sireg2} through \z{sireg6}
raise an illegal instruction exception (unless executing
in a virtual machine, covered in the next section).

@@

If extension Sscsrind is also implemented, then when \z{vsiselect} has
a value in the range \z{0x30}--\z{0x3F} or \z{0x70}--\z{0xFF},
attempts from privilege modes other than VS or VU to access alias CSRs
\z{vsireg2} through \z{vsireg6} raise an illegal instruction exception,
and attempts from VS or \mbox{VU-mode} to access \z{sireg2}
through \z{sireg6} or \z{vsireg2} through \z{vsireg6}
raise a virtual instruction exception.
